Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-08-15 main/doc/chord_sysprops.tex
minor (added documentation + fixed javadoc tags)

\subsection{Program Scope Properties}

@@

\item
\code{chord.scope.kind} \\
{\bf Type:} [\code{dynamic}$|$\code{rta}$|$\code{cha}] \\
{\bf Description:} Algorithm to compute analysis scope (i.e., reachable classes and methods).  Current choices include {\tt dynamic} (dynamic analysis), {\tt rta} (static Rapid Type Analysis), and {\tt cha} (static Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta}

\item
\code{chord.ch.kind} \\
{\bf Type:} [\code{static}$|$\code{dynamic}] \\
{\bf Description:} Algorithm to build the class hierarchy.  If it is {\tt dynamic}, then the given program is executed and classes not loaded by the JVM while running the program are excluded while building the class hierarchy.  This property is relevant only if \code{chord.scope.kind} is {\tt cha} since only this scope computing algorithm queries the class hierarchy. \\
{\bf Default value:} {\tt static}

@@

\subsection{Chord Instrumentation Properties}

@@

\item
\code{chord.trace.kind} \\
{\bf Type:} [\code{none}$|$\code{full}$|$\code{pipe}] \\
{\bf Description:} The medium to store dynamic traces (none, regular file, or POSIX pipe). \\
{\bf Default value:} {\tt full}

>>>>

\subsection{Program Scope Properties}
\label{sec:scope-props}

@@

\item
\code{chord.scope.kind} \\
{\bf Type:} {\tt [dynamic|rta|cha]} \\
{\bf Description:} Algorithm to compute analysis scope (i.e., reachable classes and methods).  Current choices include {\tt dynamic} (dynamic analysis), {\tt rta} (static Rapid Type Analysis), and {\tt cha} (static Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta}

\item
\code{chord.ch.kind} \\
{\bf Type:} {\tt [static|dynamic]} \\
{\bf Description:} Algorithm to build the class hierarchy.  If it is {\tt dynamic}, then the given program is executed and classes not loaded by the JVM while running the program are excluded while building the class hierarchy.  This property is relevant only if \code{chord.scope.kind} is {\tt cha} since only this scope computing algorithm queries the class hierarchy. \\
{\bf Default value:} {\tt static}

@@

\subsection{Chord Instrumentation Properties}
\label{sec:instr-props}

@@

\item
\code{chord.trace.kind} \\
{\bf Type:} {\tt [none|full|pipe]} \\
{\bf Description:} The medium to store dynamic traces (none, regular file, or POSIX pipe). \\
{\bf Default value:} {\tt full}

### 2010-08-15 main/doc/deadlock.tex
minor (added documentation + fixed javadoc tags)

Run the deadlock analysis provided in Chord by running the following command in Chord's \verb+main/+ directory:

\begin{quote}
\begin{verbatim}
prompt> ant -Dchord.work.dir=<...> -Dchord.run.analyses=deadlock-java run
\end{verbatim}
\end{quote}

where directory \verb+<...>+ contains a file named \verb+chord.properties+ which 
defines properties \verb+chord.main.class+, \verb+chord.class.path+, and \verb+chord.src.path+.
See Section \ref{sec:chord-sysprops} for the meaning of these properties.

Directory \verb+main/examples/deadlock_test/+ provides a toy Java program on which you can run the deadlock
analysis by first running \verb+ant+ in that directory (in order to compile the program's \verb+.java+ files to
\verb+.class+ files) and then running the following command in Chord's \verb+main/+ directory:

\begin{quote}
\begin{verbatim}
prompt> ant -Dchord.work.dir=examples/deadlock_test/ -Dchord.run.analyses=deadlock-java run
\end{verbatim}
\end{quote}

Upon successful completion, the file \verb+deadlocks.html+ should be produced in directory
\verb+main/examples/deadlock_test/chord_output/+.

>>>>

Run the deadlock analysis provided in Chord by running the following command in Chord's {\tt main/} directory:

\begin{verbatim}
    prompt> ant -Dchord.work.dir=<...> -Dchord.run.analyses=deadlock-java run
\end{verbatim}

\noindent where directory {\tt <...>} contains a file named \code{chord.properties} which
defines properties \code{chord.main.class}, \code{chord.class.path}, and \code{chord.src.path}.
See Section \ref{sec:chord-sysprops} for the meaning of these properties.

Directory \code{main/examples/deadlock_test/} provides a toy Java program on which you can run
the deadlock analysis.
First run {\tt ant} in that directory (in order to compile the program's {\tt .java} files to
{\tt .class} files) and then run the above command in Chord's {\tt main/} directory with
{\tt <...>} replaced by \code{examples/deadlock_test/}.
Upon successful completion, the file \code{deadlocks.html} should be produced in directory
\code{main/examples/deadlock_test/chord_output/}.
